Bayesian Sparsification of Deep $\cplx$-valued networks

### 2020-02-06 paper/paper.tex
added proper plot placeholders

\begin{figure}[ht]
  \centering
  \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
  \caption{%
    Smoothed density of $\log\alpha$ for a convolutional and dense layer from the
    model in sec.~\ref{sub:mnist_like_datasets}.
  }
  \label{fig:log-alpha__mnist-like}
\end{figure}

@@

% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
Figures~\ref{fig:mnist-like__trade-off__vd} and ~\ref{fig:mnist-like__trade-off__ard} show
the results on the ``MNIST'' dataset for $\tau\in\{-\tfrac12, \tfrac32\}$ and $
  C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
$ replicated $5$ times using the method from sec.~\ref{ssub:variational_dropout} (VD)
and~\ref{ssub:empirical_bayes} (ARD), respectively (results for other MNIST-like datasets
are in the appendix).

@@

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__TwoLayerDenseModelVD.pdf}
    % \caption{} \label{fig:log-alpha-kde}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__SimpleConvModelVD.pdf}
    % \caption{} \label{fig:log-alpha-proba}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
    (top) and \textit{SimpleConvModel} (bottom) for method in sec.~\ref{ssub:variational_dropout}.
  }
  \label{fig:mnist-like__trade-off__vd}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__TwoLayerDenseModelARD.pdf}
    % \caption{} \label{fig:log-alpha-kde}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__SimpleConvModelARD.pdf}
    % \caption{} \label{fig:log-alpha-proba}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
    (top) and \textit{SimpleConvModel} (bottom) for method in sec.~\ref{ssub:empirical_bayes}.
  }
  \label{fig:mnist-like__trade-off__ard}
\end{figure}

@@

% compare compressed cplx-vgg against real-vgg

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-fine-tune.pdf}
    % \caption{} \label{fig:log-alpha-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v2-fine-tune.pdf}
    % \caption{} \label{fig:log-alpha-proba}
  \end{subfigure}
  \caption{%
    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
    uncompressed model.
    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{orange} VD}
    (\ref{ssub:variational_dropout}) and \textbf{\color{blue} ARD} (\ref{ssub:empirical_bayes});
    \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet_trade-off}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-trade-off.pdf}
    % \caption{} \label{fig:log-alpha-kde}
  \end{subfigure} \\
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-trade-off.pdf}
    % \caption{} \label{fig:log-alpha-proba}
  \end{subfigure}
  \caption{%
    Pre ``fine-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
  }
  \label{fig:musicnet_trade-off_pre_fune-tune}
\end{figure}
% subsection muscinet (end)

>>>>

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
  \end{subfigure}
  \caption{%
    Smoothed density of $\log\alpha$ for a convolutional and dense layer from a model
    in sec.~\ref{sub:mnist_like_datasets}.
  }
  \label{fig:log-alpha__mnist-like}
\end{figure}

@@

% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
Plots on figure~\ref{fig:mnist-like__trade-off} show the results on the ``MNIST'' dataset for
$\tau\in\{-\tfrac12, \tfrac32\}$ and $
  C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
$ replicated $5$ times using the method from sec.~\ref{ssub:variational_dropout} (VD)
and~\ref{ssub:empirical_bayes} (ARD), respectively (results for other MNIST-like datasets
are in the appendix).

@@

% a couple of plots from MNIST and Fashion-MNIST
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
    (top) and \textit{SimpleConvModel} (bottom) for methods in sections~\ref{ssub:variational_dropout}
    and~\ref{ssub:empirical_bayes}.
  }
  \label{fig:mnist-like__trade-off}
\end{figure}

@@

% compare compressed cplx-vgg against real-vgg
\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__cifar10__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__cifar10__threshold/cifar10__threshold.pdf}
  \end{subfigure}
  \caption{%
    Pre ``fine-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
  }
  \label{fig:figure__cifar10__trade-off}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__trade-off/legacy__musicnetram__fft__-0.5.pdf}
  \end{subfigure} \\%
  % \hfill
  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
    \centering
    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__threshold/threshold.pdf}
  \end{subfigure}
  \caption{%
    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
    uncompressed model.
    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{blue} VD}
    (\ref{ssub:variational_dropout}) and \textbf{\color{orange} ARD} (\ref{ssub:empirical_bayes});
    \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
  }
  \label{fig:musicnet__trade-off}
\end{figure}

% subsection muscinet (end)
